Hydra Battles and Cie

### 2021-01-18 doc/chapter-primrec.tex
redaction of Ackermann chapter (continued)

@@

>>>>

Please note that the projection $\pi_{1,1}$ is just the identity on \texttt{nat}, and is realized by 
(\texttt{projFunc 1 0}).

\vspace{4pt}
\noindent
\emph{From \href{../theories/html/hydras.Ackermann.primRec.html}{Ackermann.primRec}.}

\begin{Coqsrc}
Lemma idIsPR : isPR 1 (fun x : nat => x).
Proof.
  assert (H: 0 < 1) by auto.
  exists (projFunc 1 0 H); cbn; auto.
Qed.
\end{Coqsrc}

@@

\begin{todo}
Comment more examples from   \href{../theories/html/hydras.Ackermann.PrimRecExamples.html}{Ackermann.PrimRecExamples}.
\end{todo}

\section{Two challenges}

\begin{itemize}
\item Write a simple and readable proof that the Fibonacci function is primitive recursive.

We give the tail-recursive definition from~\cite{BC04}, chapter 9. See also
\href{https://coq-community.org/coq-art/ch9_function_specification/SRC/fib_tail.v}{this file}.
\begin{Coqsrc}

Fixpoint general_fib (a0 a1 n:nat) {struct n} : nat :=
  match n with
  | O => a0
  | S p => general_fib a1 (a0 + a1) p
  end.

Definition fib_tail (n:nat) := general_fib 1 1 n.
\end{Coqsrc}

\item Prove formally that the Ackermann function is \emph{not} primitive recursive.

\end{itemize}
